Estimating migration rates for iteroparous species using kinship pairs found between populations

### 2021-09-28 latex/ms.tex
complete #7, and change variable name in .R

To estimate the migration number or rate, we utilize the number of HS and/or PO pairs observed in a sample. In the both populations, $n_{\rm O, 1}$ and $n_{\rm O, 2}$ offspring are randomly sampled, which are identified as young-of-year individuals without errors. Additionally, $n_{\rm P, 1}$ and $n_{\rm P, 2}$ parents are randomly sampled immediately after the end of the reproductive season in the first and second year, respectively. For mathematical tractability, parents have to survive during the reproductive season; therefore, both mother and father of a certain offspring have a potential to be sampled even in the same year. It should be noted that all the four kinds of a sample (i.e., $n_{\rm P, 1}$, $n_{\rm P, 2}$, $n_{\rm O, 1}$, and $n_{\rm O, 2}$) are not always required for estimating migration number or rate; what kinds of a sample are needed depends on the situation, as explained later. Up to the subsection 2.6, we only focus HS pairs and PO pairs found between the two populations. For the applicability of fishery management, we assume invasive sampling procedure, preventing the finding of a parent-offspring pair such that a parent and offspring is sampled in the population 1 and 2, respectively.

@@

@@

\renewcommand{\arraystretch}{0.6}
\begin{table}[tb]
\begin{center}
   \caption[]{Table 1: The list of mathematical symbols employed in the main text}
    \textbf {}\\[-4mm]
    \begin{tabular}{llc} \hline
       & & \\
	$n_{\rm P,1}, n_{\rm P, 2}$			& Sample number of parents in the population 1 and 2\\ 
		                						& \\
	$n_{\rm O, 1}, n_{\rm O, 2}$			& Sample number of offspring in the population 1 and 2\\ 
		                						& \\
	$N_{1}, N_{2}$						& Number of parents in the population 1 and 2 when sampled offspring are born\\
		                						& \\
	$M$								& Number of survived migrants of parents from the population 1 to population 2\\
		                						& \\
	$r$								& Sex ratio\\
		                						& \\
	$\pi_{\rm PO,1}, \pi_{\rm PO,2}$		& Probability that a randomly selected pair (mother and offspring) \\
	                							& shares a parent-offspring relationship within the population 1 and 2\\
									& \\
	$\pi_{\rm PO, bet}$					& Probability that a randomly selected pair (parent and offspring in the population 1 and 2, \\
	                							& respectively) shares a parent-offspring relationship between the population 1 and 2\\
									& \\
	$\pi_{\rm HS, bet}$					& Probability that a randomly selected pair (two offspring in the population 1 and 2) \\
	                							& shares a half-sibling relationship between the population 1 and 2\\
					                			& \\
	$\lambda_{i,1}, \lambda_{j,2}$			& Expected number of surviving offspring of parent $i$ and $j$ at sampling in the population 1 and 2\\
		                						& \\
	$\lambda_{i, M}$					& Expected number of surviving offspring of migrant $i$ at sampling\\
		                						& \\
	$k_{i,1}, k_{j,2}$					& Number of surviving offspring born to parent $i$ and $j$ in the population 1 and 2\\ 
	                							& \\
	$H_{\rm PO, 1}, H_{\rm PO, 2}$		& Number of parent-offspring pairs observed in samples within the population 1 and 2\\ 
	                							& \\
	$H_{\rm PO, bet}$					& Number of parent-offspring pairs observed in samples between the population 1 and 2\\ 
	                							& \\
	$H_{\rm HS, bet}$					& Number of half-sibling pairs observed in samples between the population 1 and 2\\ 
	                							& \\              		
	\hline
    \end{tabular}
    \label{symbols} 
\end{center} 
\end{table}
\renewcommand{\arraystretch}{1}

>>>>

To estimate the migration number or rate, we utilize the number of HS and/or PO pairs observed in a sample. In the both populations, $n_{\rm O, 1}$ and $n_{\rm O, 2}$ offspring are randomly sampled in the first and second year, respectively, which are identified as young-of-year individuals without errors. Additionally, $n_{\rm P, 1}$ and $n_{\rm P, 2}$ parents are randomly sampled immediately after the end of the reproductive season in the first and second year, respectively. For mathematical tractability, parents have to survive during the reproductive season; therefore, both mother and father of a certain offspring have a potential to be sampled even in the same year. It should be noted that all the four kinds of a sample (i.e., $n_{\rm P, 1}$, $n_{\rm P, 2}$, $n_{\rm O, 1}$, and $n_{\rm O, 2}$) are not always required for estimating migration number or rate; what kinds of a sample are needed depends on the situation, as explained later. Up to the subsection 2.6, we only focus HS pairs and PO pairs found between the two populations. For the applicability of fishery management, we assume invasive sampling procedure, preventing the finding of a parent-offspring pair such that a parent and offspring is sampled in the population 1 and 2, respectively.

@@

We developed an individual-based model that tracks kinship relationships to evaluate the estimator's performance. The population structure was assumed to be identical to that in the development of the estimators. The population 1 and 2 comprised $N_1$ and $N_2$ parents with an equal sex ratio, and their offspring number was assumed to follow the geometric distribution with mean $\lambda_1$ and $\lambda_2$ (i.e., Poisson reproduction with mean $\lambda_{i,1}$ and $\lambda_{j,2}$ which follows the exponential distribution with mean $\lambda_1$ and $\lambda_2$), respectively. Migrant parents were randomly chosen from the population 1 at the end of the first year. Each offspring retained the parent's ID, making it possible to trace an HS and PO relationship.

Let a parameter set ($N_1$, $N_2$, $M$, $\lambda_1$, $\lambda_2$, $n_{\rm O,1}$, $n_{\rm O,2}$, $n_{\rm P,1}$, $n_{\rm P,2}$) be given. We simulated a population history and a sampling process, which generates proposed estimators; this process was repeated 1000 times, making it possible to construct the distribution of the estimators for each parameter set.

@@

\renewcommand{\arraystretch}{0.6}
\begin{table}[tb]
%\centering
   \caption[]{Table 1: The list of mathematical symbols employed in the main text}
    \textbf {}\\[-4mm]
    \begin{tabular}{llc} \hline
       & & \\
	$n_{\rm P,1}, n_{\rm P, 2}$			& Sampled number of parents from the population 1 and 2\\ 
		                						& \\
	$n_{\rm O, 1}, n_{\rm O, 2}$			& Sampled number of offspring from the population 1 and 2\\ 
		                						& \\
	$N_{1}, N_{2}$						& Number of parents in the population 1 and 2 when sampled offspring are born\\
		                						& \\
	$M$								& Number of survived migrants of parents from the population 1 to population 2\\
		                						& \\
	$r$								& Sex ratio\\
		                						& \\
	$\pi_{\rm PO,1}, \pi_{\rm PO,2}$		& Probability that a randomly selected pair (parent and offspring) \\
	                							& shares a parent-offspring relationship within the population 1 and 2\\
									& \\
	$\pi_{\rm PO, bet}$					& Probability that a randomly selected pair (parent and offspring) \\
	                							& shares a parent-offspring relationship between the population 1 and 2\\
									& \\
	$\pi_{\rm HS, bet}$					& Probability that a randomly selected pair (two offspring) \\
	                							& shares a half-sibling relationship between the population 1 and 2\\
					                			& \\
	$\lambda_{i,1}, \lambda_{j,2}$			& Expected number of surviving offspring of parent $i$ and $j$ at sampling in the population 1 and 2\\
		                						& \\
	$\lambda_{i, M}$					& Expected number of surviving offspring of migrant $i$ at sampling\\
		                						& \\
	$k_{i,1}, k_{j,2}$					& Number of surviving offspring born to parent $i$ and $j$ in the population 1 and 2\\ 
	                							& \\
	$H_{\rm PO, 1}, H_{\rm PO, 2}$		& Number of parent-offspring pairs observed in samples within the population 1 and 2\\ 
	                							& \\
	$H_{\rm PO, bet}$					& Number of parent-offspring pairs observed in samples between the population 1 and 2\\ 
	                							& \\
	$H_{\rm HS, bet}$					& Number of half-sibling pairs observed in samples between the population 1 and 2\\ 
	                							& \\              		
	\hline
    \end{tabular}
    \label{symbols} 
\\Subscription ``1'' and ``2'' indicates the quantity in the population 1 during the first year and in the population 2 during the second year, respectively. 
\end{table}
\renewcommand{\arraystretch}{1}
